---
title: "Data_preprocessing"
author: "Thanthirige Lakshika Ruberu"
date: "7/6/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F,message = F)
```

```{r}
#read file.
library(dplyr)
library(readxl)
datafile <- read_excel("file1.xlsx")
datafile2 <- read.csv("file3.csv",header = F)
```
DSM IV cannabis dependence 15-35 years
```{r}
dependency=datafile2[,1:17]
num=15:30
colnames(dependency)=c('id',num)



#replace-999 with NA
dependency[,2:17][dependency[,2:17]==-999]=NA

x=colSums(dependency[,2:17],na.rm = T)
x

round(x/1265,3)

#getting dependency status by calling max
dependency$diagnosis=do.call(pmax, c(dependency[,-1], na.rm =T))
table(dependency$diagnosis,useNA = 'ifany')

#computing age of diagnosis
#dependency$diag_age=as.numeric(colnames(dependency[,2:17])[apply(dependency[,2:17],1, function(x) min(which(x==1)))])
dependency$diag_age=ifelse(dependency$diagnosis==1,as.numeric(colnames(dependency[,2:17])[apply(dependency[,2:17],1, function(x) min(which(x==1)))]),as.numeric(colnames(dependency[,2:17])[apply(dependency[,2:17],1, function(x) max(which(x==0)))]))


dependency=data.frame('id'=dependency$id,'diagnosis'=dependency$diagnosis,'age_of_diagnosis'=dependency$diag_age)

min(na.omit(dependency$age_of_diagnosis))

#remove people with age 15 

```








```{r}
#gender
#1=Male
gender=datafile$gender
table(gender,useNA = 'ifany')

```

Peer Cannabis use $\\$
Available variables are$\\$
In the last year$\\$
age15/16: best friend use cannabis with 1=Yes, 2=N0$\\$
age15/16: other close friends use cannabis  1=Yes, 2=N0$\\$
age 18/21/25 :Two questions for How many of your Male/female friends Use marijuana or other drugs (Most=3/Some=2/None=1) (No timeline in question)$\\$
```{r}
#peer cannabis use:Of your 3 best friends, how many use marijuana at least once a month?

peer_cannabis_use=datafile[,(ncol(datafile)-9):ncol(datafile)] 
# note the dataset contain 0,1 for yes no variables
#for 14,15 take average of best friend and other close friends
peer_cannabis_use$age15=apply(peer_cannabis_use[,1:2],1,mean)
peer_cannabis_use$age16=apply(peer_cannabis_use[,3:4],1,mean)


#for 18,21, 25 take average of male and female friends
#recode None=0,Some=1 and Most=2
peer_cannabis_use[,5:10][peer_cannabis_use[,5:10]==1]=0
peer_cannabis_use[,5:10][peer_cannabis_use[,5:10]==2]=1
peer_cannabis_use[,5:10][peer_cannabis_use[,5:10]==3]=2

peer_cannabis_use$age18=apply(peer_cannabis_use[,5:6],1,mean)/2
peer_cannabis_use$age21=apply(peer_cannabis_use[,7:8],1,mean)/2
peer_cannabis_use$age25=apply(peer_cannabis_use[,9:10],1,mean)/2



peer_cannabis_use=data.frame('id'=datafile$a0, peer_cannabis_use[,11:15])


par(mfrow=c(1,5))
boxplot(peer_cannabis_use$age15,xlab='age15')
boxplot(peer_cannabis_use$age16,xlab='age16')
boxplot(peer_cannabis_use$age18,xlab='age18',ylim=c(0,1))
boxplot(peer_cannabis_use$age21,xlab='age21',ylim=c(0,1))
boxplot(peer_cannabis_use$age25,xlab='age25',ylim=c(0,1))



peer_cannabis_use$diagnosis=dependency$diagnosis
peer_cannabis_use$diagnosis_age=dependency$age_of_diagnosis


peer_cannabis_use$age15=ifelse(is.na(peer_cannabis_use$diagnosis_age)==T,NA,ifelse(peer_cannabis_use$diagnosis_age<15,NA,peer_cannabis_use$age15))
peer_cannabis_use$age16=ifelse(is.na(peer_cannabis_use$diagnosis_age)==T,NA,ifelse(peer_cannabis_use$diagnosis_age<16,NA,peer_cannabis_use$age16))
peer_cannabis_use$age18=ifelse(is.na(peer_cannabis_use$diagnosis_age)==T,NA,ifelse(peer_cannabis_use$diagnosis_age<18,NA,peer_cannabis_use$age18))
peer_cannabis_use$age21=ifelse(is.na(peer_cannabis_use$diagnosis_age)==T,NA,ifelse(peer_cannabis_use$diagnosis_age<21,NA,peer_cannabis_use$age21))
peer_cannabis_use$age25=ifelse(is.na(peer_cannabis_use$diagnosis_age)==T,NA,ifelse(peer_cannabis_use$diagnosis_age<25,NA,peer_cannabis_use$age25))



num=c(15,16,18,21,25)
colnames(peer_cannabis_use)=c('id',paste('peer',num,sep=''))
```
\newpage

Delinquency

Conduct problems from ages 7-16


Age 7 min 41 max 123;Age 8 min 43 max 129; age 9 min 41 max 123; age 10 min 43 max 129; age 11 min 43 max 129; age 12 min 43 max 129; age 13 min 41 max 123; age 14 min 39 max 117; age 15 min 21 max 63; age 16 min 21 max 63.

 check for ages for delinquency of controls whose age at diagnosis was 16
```{r}


#extract delinquency variables
delinquency=datafile2[,23:32]
ages=7:16
colnames(delinquency)=paste('del',ages,sep='')

#make -999 NA
delinquency[delinquency==-999]=NA
summary(delinquency)
#scaling variables 0-1
delinquency$del7=(delinquency$del7-41)/123
delinquency$del8=(delinquency$del8-43)/129
delinquency$del9=(delinquency$del9-41)/123
delinquency$del10=(delinquency$del10-43)/129
delinquency$del11=(delinquency$del11-43)/129
delinquency$del12=(delinquency$del12-43)/129
delinquency$del13=(delinquency$del13-41)/123
delinquency$del14=(delinquency$del14-39)/117
delinquency$del15=(delinquency$del15-21)/63
delinquency$del16=(delinquency$del16-21)/63

delinquency$diagnosis_age=dependency$age_of_diagnosis


delinquency$del16=ifelse(is.na(delinquency$diagnosis_age)==T,NA,ifelse(delinquency$diagnosis_age<16,NA,delinquency$del16))


#summary(delinquency)



```

\newpage

Adverse Childhood Experiences

Physical abuse before16 years: childhood physical punishment (reverse scored, higher numbers are lower levels of punishment)-birth to 16 years can use it because response is collected starting at 16 (4) parent never used physical punishment (3) parents seldom used physical punishment  (2) at least one parent regularly used physical punishment  (1) at least one parent used physical punishment  too often or too severely$\\$
$\\$

make 4=0  and others 1

```{r}
ph_abuse=datafile$physab
table(ph_abuse,useNA = 'ifany')

ph_abuse[ph_abuse==3]=1
ph_abuse[ph_abuse==2]=1
ph_abuse[ph_abuse==4]=0

table(ph_abuse,useNA = 'ifany')



```

Sexual abuse :childhood sexual abuse before age 16 
0 = none, 1 = non-contact sexual abuse; 2 = contact sexual abuse (no penetration); 3 = contact sexual abuse involving penetration.

sexually assaulted at age 17,18 (0,1 variable 0 must be no)$\\$
```{r}
se_abuse=data.frame('before16_Seabuse'=datafile$sexab,'17_Seabuse'=datafile$sxassault17,
                    '18_Seabuse'=datafile$sxassault18)
#In sexual abuse before 16 years there are 0,1,2,3 
#make 0=0 and 1,2,3=1
se_abuse$before16_Seabuse[se_abuse$before16_Seabuse==2]=1
se_abuse$before16_Seabuse[se_abuse$before16_Seabuse==3]=1

table(se_abuse$before16_Seabuse,useNA = 'ifany')

#at 17 years
table(se_abuse$X17_Seabuse,useNA = 'ifany')

#at 18 years
table(se_abuse$X18_Seabuse,useNA = 'ifany')




#at age 18 if make se_abuse NA if they are already dependent
se_abuse$diagnosis=dependency$diagnosis
se_abuse$ageofdiagnosis=dependency$age_of_diagnosis
se_abuse$X17_Seabuse=ifelse(is.na(se_abuse$ageofdiagnosis)==T,NA,ifelse(se_abuse$ageofdiagnosis<17,NA,se_abuse$X17_Seabuse))
se_abuse$X18_Seabuse=ifelse(is.na(se_abuse$ageofdiagnosis)==T,NA,ifelse(se_abuse$ageofdiagnosis<18,NA,se_abuse$X18_Seabuse))



#final variable say 1 if said 1 at any age 0 if all are not NA otherwise
se_abuse$seabuse=do.call(pmax,c(se_abuse[,1:3],na.rm = T))
se_abuse$id=datafile2$V1



```

Parental death or separation : Measured by total number of change in parental figures to age 15$\\$
```{r}
#parental seperation
P_seperation=datafile$chpar15
table(P_seperation,useNA = 'ifany')

P_seperation=ifelse(P_seperation>0,1,P_seperation)
table(P_seperation,useNA = 'ifany')
```

Parental incarceration :At age 15 years the young person's parents were asked if they had a record for criminal offending. $\\$
```{r}
p_jail=datafile$phoffend
table(p_jail,useNA = 'ifany')
```

Father alcoholism: At age 15 years the young person's parents were asked whether they had a history of alcoholism or problems with alcohol$\\$
```{r}
p_alcohol=datafile$phalc
table(p_alcohol,useNA = 'ifany')
```

```{r}
#adverse childhoood experiences

ACE=data.frame(ph_abuse,'se_abuse'=se_abuse$seabuse,P_seperation,p_jail,p_alcohol)

sumna <- function(x) {
       if(all(is.na(x))) NA else sum(x, na.rm = TRUE)
}
countna <- function(x) {
       if(all(is.na(x))) NA else length(na.omit(x))
}

ACE$status=apply(ACE,1,sumna)

ACE$countna=apply(ACE[,1:5],1,countna)

ACE$status_final=ACE$status/ACE$countna


```



\newpage

Personality_variables$\\$
neuroticism age 14$\\$
maximum possible value is 30
novelty seeking age 16$\\$
maximum possible value is 31
conscientiousness (measured ONLY AT THIS AGE)$\\$
These scales range from 4 to 12
```{r}
n_sum=(datafile$epin14-10)/30
summary(n_sum)


i_sum=datafile$resns/31
summary(i_sum)

c_sum=(datafile$conscientiousness40-4)/12
summary(c_sum)

par(mfrow=c(1,3))

```



```{r,echo=F}
#final datasets

#cross scetional variables
final_Data=data.frame('id'=dependency$id,'diagnosis'=dependency$diagnosis,'gender'=gender,'ACE'=ACE$status_final,'n_sum'=n_sum,'i_sum'=i_sum,'c_sum'=c_sum,peer_cannabis_use[,2:6],delinquency)

final_Data_complete=final_Data[complete.cases(final_Data[,2:7]), ]


#remove people with all missing values for all waves in peer cannabis use
#extract variables
peer <- final_Data_complete %>% select(c(starts_with("peer")))
#checking whether there are variables with missing values at each age
peer$missing_values= apply(peer,1,function(x) sum(is.na(x)))
#extract IDS whose values are missing
peer_missing=peer %>%filter(peer$missing_values==5) #no missing values in all

#remove people with all missing values for all waves in delinquency
#extract variables
delq <- final_Data_complete %>% select(c(starts_with("del")))
#checking whether there are variables with missing values at each age
delq$missing_values= apply(delq,1,function(x) sum(is.na(x)))
#extract IDS whose values are missing
delq_missing=peer %>%filter(delq$missing_values==10) #no missing values in all




```

```{r}
#dealing with the users

users=read.csv('file12.csv',header = F)

#2nd variable = 13 year interview 1/2
#3rd=14 year interview 1/2
#4th/5th-15:16 year interview
# 25-29 variables - Since you turned 18/21/25/30/35, have you ever used or tried smoking cannabis
 
users=subset(users,users$V1 %in% final_Data_complete$id)


#for 15 and 16 if >o make them 1

users_use=users[,c(2:19)]
num=c(13:30)
colnames(users_use)=c(num)

users_use$`13`=ifelse(users_use$`13`==2,0,users_use$`13`)
users_use$`14`=ifelse(users_use$`14`==2,0,users_use$`14`)

users_use$`15`=ifelse(users_use$`15`>0,1,users_use$`15`)
users_use$`16`=ifelse(users_use$`16`>0,1,users_use$`16`)





#extracting variables corresponding to age 18
variables_18=users[,c(6,7,25)]
variables_18$numberofuse=do.call(pmax, c(variables_18[,-3], na.rm = TRUE)) # get the maximum number of use in 17,18
table(variables_18$V25,variables_18$numberofuse) # check weather 2 in have used correspond to number of uses being 0
#in 17,18 0 corresponds to non use

users_use$`17`=ifelse(users_use$`17`>0,1,users_use$`17`)
users_use$`18`=ifelse(users_use$`18`>0,1,users_use$`18`)


variables_21=users[,c(8,9,10,26)]
variables_21$numberofuse=do.call(pmax, c(variables_21[,-4], na.rm = TRUE)) # get the maximum number of use in 17,18
table(variables_21$V26,variables_21$numberofuse) # check weather 2 in have used correspond to number of uses being 0
##here 99 seems to be not applicable
#in 19,20,21, 99 corresponds to non use 

users_use$`19`=ifelse(users_use$`19`==99,0,users_use$`19`)
users_use$`20`=ifelse(users_use$`20`==99,0,users_use$`20`)
users_use$`21`=ifelse(users_use$`21`==99,0,users_use$`21`)
users_use$`19`=ifelse(users_use$`19`>0,1,users_use$`19`)
users_use$`20`=ifelse(users_use$`20`>0,1,users_use$`20`)
users_use$`21`=ifelse(users_use$`21`>0,1,users_use$`21`)



variables_25=users[,c(11,12,13,14,27)]
variables_25$numberofuse=do.call(pmax, c(variables_25[,-5], na.rm = TRUE)) # get the maximum number of use in 17,18
table(variables_25$V27,variables_25$numberofuse) # check weather 2 in have used correspond to number of uses being 0
## in 22,23,24,25 here 9 seems to be not applicable which means non users

users_use$`22`=ifelse(users_use$`22`==9,0,users_use$`22`)
users_use$`23`=ifelse(users_use$`23`==9,0,users_use$`23`)
users_use$`24`=ifelse(users_use$`24`==9,0,users_use$`24`)
users_use$`25`=ifelse(users_use$`25`==9,0,users_use$`25`)
users_use$`22`=ifelse(users_use$`22` >0,1,users_use$`22`)
users_use$`23`=ifelse(users_use$`23`>0,1,users_use$`23`)
users_use$`24`=ifelse(users_use$`24`>0,1,users_use$`24`)
users_use$`25`=ifelse(users_use$`25`>0,1,users_use$`25`)


variables_30=users[,c(15,16,17,18,19,28)]
variables_30$numberofuse=do.call(pmax, c(variables_30[,-6], na.rm = TRUE)) # get the maximum number of use in 17,18
table(variables_30$V28,variables_30$numberofuse) 
users_use$`26`=ifelse(users_use$`26`>0,1,users_use$`26`)
users_use$`27`=ifelse(users_use$`27`>0,1,users_use$`27`)
users_use$`28`=ifelse(users_use$`28`>0,1,users_use$`28`)
users_use$`29`=ifelse(users_use$`29`>0,1,users_use$`29`)
users_use$`30`=ifelse(users_use$`30`>0,1,users_use$`30`)

# check weather 2 in have used correspond to number of uses being 0
#from 25 -30 0 is non users

#take age of first use
users_use$status=do.call(pmax, c(users_use, na.rm = TRUE))
users_use$age=as.numeric(colnames(users_use[,1:18])[apply(users_use[,1:18],1, function(x) min(which(x==1)))])
users_use$diagnosis_age=final_Data_complete$diagnosis_age

users_use2=subset(users_use,users_use$status==1)

users_use2$final=ifelse(users_use2$age<=users_use2$diagnosis_age,1,0) #check with diagnosis age
table(users_use2$final)
```

```{r}
#combining final_Data and user_data
final_Data_complete$use_status=users_use$status

table(final_Data_complete$use_status,useNA = 'ifany') #no missing values in use status
final_Data_complete=subset(final_Data_complete,final_Data_complete$use_status==1)


```



\newpage

Summaries from the final dataset
Number of cases and controls
```{r}

write.csv(final_Data_complete,'final_data_CHDS_302.csv')
table(final_Data_complete$diagnosis)
105/637 #16.48%
```

Gender-Male=1
```{r}
table(final_Data_complete$gender)
319/637 #%50.07 males
100-50.07
table(final_Data_complete$gender,final_Data_complete$diagnosis)
74/(74+31)
100-70.48

245/(245+287)
100-46.05
```

Summary Statistics

```{r}
#ACE
round(final_Data_complete %>% group_by(diagnosis) %>% summarise ( me=mean(ACE),std=sd(ACE)),2)
round(final_Data_complete %>% summarise ( me=mean(ACE),std=sd(ACE)),2)

#nsum
round(final_Data_complete %>% group_by(diagnosis) %>% summarise ( me=mean(n_sum),std=sd(n_sum)),2)
round(final_Data_complete %>% summarise ( me=mean(n_sum),std=sd(n_sum)),2)

#csum
round(final_Data_complete %>% group_by(diagnosis) %>% summarise ( me=mean(c_sum),std=sd(c_sum)),2)
round(final_Data_complete %>% summarise ( me=mean(c_sum),std=sd(c_sum)),2)

#isum
round(final_Data_complete %>% group_by(diagnosis) %>% summarise ( me=mean(i_sum),std=sd(i_sum)),2)
round(final_Data_complete %>% summarise ( me=mean(i_sum),std=sd(i_sum)),2)


#delinquency
delq <- final_Data_complete %>% select(c(starts_with("del")))
delq$sum=apply(delq,1,  sumna)
delq$count=apply(delq[,-11],1,  countna)

delq$score=delq$sum/delq$count
delq$diagnosis=final_Data_complete$diagnosis

round(delq %>% group_by(diagnosis) %>% summarise ( me=mean(score),std=sd(score)),2)
round(delq%>% summarise ( me=mean(score),std=sd(score)),2)

#peer Cannabis use

#calculate random effects for peer
peer <- final_Data_complete %>% select(c(starts_with("peer")))
peer$target=final_Data_complete$id
#getting ages
peer$peer15_age=15
peer$peer16_age=16
peer$peer18_age=18
peer$peer21_age=21
peer$peer25_age=25

#MAking ages NA if the corresponding value is NA

peer$peer15_age=ifelse(is.na(peer$peer15)==T,NA,peer$peer15_age)
peer$peer16_age=ifelse(is.na(peer$peer16)==T,NA,peer$peer16_age)
peer$peer18_age=ifelse(is.na(peer$peer18)==T,NA,peer$peer18_age)
peer$peer21_age=ifelse(is.na(peer$peer21)==T,NA,peer$peer21_age)
peer$peer25_age=ifelse(is.na(peer$peer25)==T,NA,peer$peer25_age)

#reshaping the data 
#this may need to change based on the number of lonigitudinal waves

chds_pred_long_reshape_bfmj=reshape(peer,direction = "long",
                               varying = list(c("peer15","peer16","peer18","peer21","peer25"),
                                              c("peer15_age","peer16_age","peer18_age","peer21_age","peer25_age")),
                               v.names = c("no_bf_mj","age"))



chds_pred_long_reshape_bfmj=chds_pred_long_reshape_bfmj[order(chds_pred_long_reshape_bfmj$target),]
chds_pred_long_reshape_bfmj=(na.exclude(chds_pred_long_reshape_bfmj)) 

chds_pred_long_reshape_bfmj$age_sqr=chds_pred_long_reshape_bfmj$age^2



#calculation of subject specific random effects  for no of friends who use cannabis

#max_id= maximum id  number is this example, it is 423
#data_bfmj= data_frame that stored random intercepts for no_bf_mj and age for 

#####
cal_bfmj_rand <- function(max_id, data_bfmj,mean_age,sd_age){
data_final= replicate(max_id,NA)
s1_mjcent=list()
a_new_sub=list()
b_new_sub=list()
A_prod_sub=list()
diag_sub=list()
v_sub=list()

b_new_sub=list()
b_renew_sub_mj_cent=list()
#a_bfmj<-c(-2.1994286,0.2728788,-0.0074255)
a_bfmj<-c(0.243510,0.045512,-0.023522)
sigma_u_bfmj <- 0.047829
sigma_e_bfmj <- 0.054666

G<- sigma_u_bfmj

offdiag_bfmj<-sigma_u_bfmj



for(i in c(1:max_id)){
  s1_mjcent[[i]]=subset(data_bfmj, data_bfmj$id==i)
  #input mean and sd of age for the new data
  s1_mjcent[[i]]$age_cent <- (s1_mjcent[[i]]$age-mean_age)/sd_age
  s1_mjcent[[i]]$age_centqd <- (s1_mjcent[[i]]$age_cent )^2
  
  a_new_sub[[i]] <- cbind(rep(1,dim(s1_mjcent[[i]])[1]),s1_mjcent[[i]]$age_cent,s1_mjcent[[i]]$age_centqd
                          )
  b_new_sub[[i]]<-as.matrix(rep(1,dim(s1_mjcent[[i]])[[1]]))
  A_prod_sub [[i]] <- a_new_sub[[i]]%*%a_bfmj
  
  diag_sub[[i]] <- rep(sigma_u_bfmj +sigma_e_bfmj,dim(s1_mjcent[[i]])[1])
  
  v_sub[[i]]<- matrix(NA,ncol = length(diag_sub[[i]]),nrow=length(diag_sub[[i]]))
  v_sub[[i]][lower.tri(v_sub[[i]])]<-offdiag_bfmj
  v_sub[[i]][upper.tri(v_sub[[i]])]<-offdiag_bfmj
  diag(v_sub[[i]])<-diag_sub[[i]]
  b_renew_sub_mj_cent[[i]]<- G*t(b_new_sub[[i]])%*%solve(v_sub[[i]])%*%(s1_mjcent[[i]]$no_bf_mj-A_prod_sub[[i]])
 
data_final[i]   <-  unlist(b_renew_sub_mj_cent[[i]]) 
}
data_final1<-data.frame(cbind(unique(data_bfmj$target),data_final))
colnames(data_final1)=c("target","no_bf_mj")
return(data.frame(data_final1))
}



#evaluating the function
mean_age=16.64445
sd_age=1.787426


b_bfmj_sub_cent_nr1<-(cal_bfmj_rand(637,chds_pred_long_reshape_bfmj,mean_age,sd_age))


peer$random_effects=b_bfmj_sub_cent_nr1$no_bf_mj

peer$diagnosis=final_Data_complete$diagnosis


round(peer %>% group_by(diagnosis) %>% summarise ( me=mean(random_effects),std=sd(random_effects)),2)
round(peer %>% summarise ( me=mean(random_effects),std=sd(random_effects)),2)
```


ACE
```{r,echo=F,eval=F}
pdf('ACE_CHDS_30.pdf')
par(mfrow=c(1,2))
boxplot(final_Data_complete$ACE~final_Data_complete$diagnosis,xlab='diagnosis',ylab = 'ACE',main='CHDS',ylim=c(0,1),col=NULL)
dev.off()

pdf('c_sum_CHDS_30.pdf')
par(mfrow=c(1,2))
boxplot(final_Data_complete$c_sum~final_Data_complete$diagnosis,xlab='diagnosis',ylab = 'c_sum',main='CHDS',ylim=c(0,1),col=NULL)
dev.off()

pdf('n_sum_CHDS_30.pdf')
par(mfrow=c(1,2))
boxplot(final_Data_complete$n_sum~final_Data_complete$diagnosis,xlab='diagnosis',ylab = 'n_sum',main='CHDS',ylim=c(0,1),col=NULL)
dev.off()

pdf('i_sum_CHDS_30.pdf')
par(mfrow=c(1,2))
boxplot(final_Data_complete$i_sum~final_Data_complete$diagnosis,xlab='diagnosis',ylab = 'i_sum',main='CHDS',ylim=c(0,1),col=NULL)
dev.off()


peer <- final_Data_complete %>% select(c(starts_with("peer")))
peer$sum=apply(peer,1,  sumna)
peer$count=apply(peer[,-6],1,  countna)

peer$score=peer$sum/peer$count
pdf('peer_CHDS_30.pdf')
par(mfrow=c(1,2))
boxplot(peer$score~final_Data_complete$diagnosis,xlab='diagnosis',ylab = 'Peer cannabis use',main='CHDS',ylim=c(0,1),col=NULL)
dev.off()


pdf('delq_CHDS_30.pdf')
par(mfrow=c(1,2))
boxplot(delq$score~final_Data_complete$diagnosis,xlab='diagnosis',ylab = 'Delinquency',main='CHDS',ylim=c(0,1),col=NULL)
dev.off()


```


